Ribosome accumulation during early phase resistance training

### 2020-09-14 manuscript.Rmd
misc updates
figure 3 in draft shape

@@

>>>>

UBF levels determine rRNA gene activity throgh regulation of chromatin[@RN2556] <!--  Sanij 2008 -->

@@

**Figure 3.** mRNA (A and B) and protein abundances (C and D) of ribosomal protein S6 and Upstream bindning factor (UBF). mRNA abundaces are expressed per total RNA (round points) or per muscle weight (triangles). Black points and error bars represents statistically robust results (a 95% CI not containing 0). E shows western-blots and total protein stains from a representative participant.
